Short Paper \\\large{A Short Subtitle}

### 2023-04-05 manuscript/manuscript.tex
Figures and tables added

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

@@

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, boxrule=0pt, enhanced, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi

@@

Queen's, simply, produces an immense amount of waste that it is unable
to efficiently manage. The dozens of wards, offices, and kitchens,
serving the hundreds of patients and staff, generates considerable
infectious medical waste, mixed domestic and office waste, and kitchen
waste, which needs to be removed and disposed of daily. Some individual
wards implement waste separation, binning medical wastes separately from
general waste, however separation ends at the point of collection.
Queen's is not served by regular municipal waste collection. What
municipal collection that is done is ad-hoc, sporadic, and based on the
hospital's available financial resources. Rather, most hospital waste
(infectious and non-infectious) is gathered by grounds staff and burnt
at the hospital's incinerator, located at a central point within the
hospital campus \citep{kalina2020this}. However, the vast majority of
the deposited waste is not incinerated, as a new incinerator provided by
the Ministry of Health in late 2019, is only able to handle a small
percentage of the hospital's waste. Furthermore, the incinerator is
frequently inoperable, under repair, or without power,. Rather, the
waste is openly burned, in a constantly smouldering pile to the side of
the incinerator building, sending up the aforementioned clouds of smoke,
which choke the grounds (Figure 1). Innumerable other, smaller, fires,
scattered across the QECH campus (Figure 2) contribute their part, as
grounds and maintenance staff habitually burn leaves and other garden
refuse. Furthermore, caregivers who reside separately on hospital
grounds, cook for themselves throughout the day and night using biomass
(charcoal or wood), and burn their own domestic waste. As a result, air
quality at the hospital is a constant source of discussion, with
patients, staff, and caregivers struggling to cope, when just breathing
is, as the quote used in the title of this article, `unbearable.'

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Figure 1: Open burning at QECH, with the old incinerator building in the background (Authors).}
\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{include\_graphics}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"manuscript/img/image{-}replace{-}tree.png"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

{\centering \includegraphics{img/image-replace-tree.png}

@@

@@

\begin{itemize}
\item
  \textbf{Lions Sight First Eye Hospital}, often shortened to
  \textbf{Lions Sight}, is the largest eye hospital in Malawi and serves
  as the main teaching eye hospital for the Kamuzu University of Health
  Sciences (formerly College of Medicine). It is staffed by 5
  consultants and a team of clinical officers and nurses. It provides a
  mix of public (no cost) and private (at cost) services.
\item
  \textbf{The Blantyre Malaria Project (BMP)}, established by Professors
  Terrie Taylor and Malcolm Molyneux, has carried out clinical research
  and patient care in the area of paediatric malaria, specifically
  cerebral malaria, for more than 30 years. Its research infrastructure
  includes an administrative team, an inpatient research ward, an MRI
  centre, and an outpatient research clinic in Ndirande township and in
  other districts outside of Blantyre.
\item
  \textbf{Ward 6B} is a male ward for trauma and orthopaedic patients.
  It was established as part of the original hospital design. It is a
  60-bed ward with a dedicated nursing station and treatment rooms.
\item
  \textbf{The Blantyre Lighthouse Trust Clinic}, also known as
  \textbf{Umodzi Family Centre} or simply, the \textbf{Lighthouse
  Clinic}, is one of four operating across Malawi. The clinics work in
  collaboration with the Ministry of Health (MOH) to provide integrated
  HIV testing, treatment and care for people living with HIV.
\item
  The \textbf{Moyo Nutritional Rehabilitation and Research Unit}, known
  on campus as \textbf{uMoyo}, is a 57-bed nutritional rehabilitation
  unit (NRU) for treating infants and children with severe malnutrition
  and acute illnesses. It is one of 104 operational NRUs in Malawi. It
  also has an outpatient therapeutic feeding program (OTP) for children
  with malnutrition who can be treated outside of the hospital.
\item
  \textbf{Mercy James Institute for Pediatric Surgery and Intensive Care
  (MJC)}, shortened on campus to \textbf{Mercy James}, was opened in
  2017 by the NGO Raising Malawi, which was founded by Madonna. With 3
  operating rooms and 50 beds, it is the first and only first dedicated
  paediatric surgery hospital in Malawi. Prior to its opening, QECH had
  fewer than 10 intensive care beds.
\item
  The \textbf{Administration Building} is the operational hub of the
  campus, containing mostly offices and meeting rooms.
\item
  When a patient arrives at QECH, she or he will usually arrive with a
  guardian: someone to cook for them, buy medicine, do their laundry,
  and help them bathe. The \textbf{Guardian Shelter} is a
  gender-separated concrete floor shelter for sleeping along with a
  cooking pavilion and toilet/shower block are maintained by a local
  NGO. Though simple, the facility is secure and offers one of the only
  free/accessible toilet facilities for visitors on the QECH campus.
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# map}
\CommentTok{\# Figure 2: Sensor locations within QECH}
\end{Highlighting}
\end{Shaded}

@@

Therefore, for international comparisons and due to the lack of
comprehensive Malawian Standards, we use the WHO recommendations as a
basis of comparison for the measured values
\citep{worldhealthorganization2021who}. The relevant particulate matter
targets are presented in Table 1.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Table 1. Particulate matter targets from @worldhealthorganization2021who}
\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{include\_graphics}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"manuscript/img/image{-}replace{-}table.png"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{figure}[H]

{\centering \includegraphics{img/image-replace-table.png}

@@

@@

Due to localised variation (air movement in the immediate area) and the
density of the observations, the plotted 5-minute data obscure
persistent trends. The full set of 5-minute data are plotted and
presented in Appendix XA1 (TODO). However, the number of measured values
that exceeded the hazardous limit for both parameters are summarised in
Table 2.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Table 2. Peaks for both PM2.5 and PM10 are the number of data points above the WHO interim target 1 (annual) which is the least stringent;  the number of observations recorded (count) is provided for reference. }
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Figure 3. Average 24{-}hour PM10 and PM2.5 at 8 monitoring stations over 2 months}
\end{Highlighting}
\end{Shaded}

@@

Given that the type of fuel and the type of burning (contained vs.~open)
produce very different particulate ``fingerprints'', the ratio of PM10
to PM2.5 values were examined to determine if a clear difference between
locations, and therefore source, could be identified. The results are
presented in Figure 4.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Figure 4. PM10:PM2.5 values for each location.  Each line shows the minimum and maximum ratio for the day based on ratios calculated hourly.  }
\end{Highlighting}
\end{Shaded}

@@

The relative amount of time exposed to a given category of air quality
is shown in Figure 5. Each square represents 1\% of the measured time.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Figure 5. Percentage of measured values categorised according to WHO 2021 targets}
\end{Highlighting}
\end{Shaded}

@@

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

@@

\hypertarget{figures-and-tables}{%
\section{Figures and tables}\label{figures-and-tables}}

Figure~\ref{fig-meaningless} is generated using an R chunk.

@@

{\centering \includegraphics[width=0.5\textwidth,height=\textheight]{manuscript_files/figure-pdf/fig-meaningless-1.pdf}

@@

\caption{\label{fig-meaningless}A meaningless scatterplot}

@@

\hypertarget{tables-coming-from-r}{%
\section{Tables coming from R}\label{tables-coming-from-r}}

Tables can also be generated using R chunks, as shown in
Table~\ref{tbl-simple} example.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}\FunctionTok{head}\NormalTok{(mtcars)[,}\DecValTok{1}\SpecialCharTok{:}\DecValTok{4}\NormalTok{])}
\end{Highlighting}
\end{Shaded}

\hypertarget{tbl-simple}{}
\begin{longtable}[]{@{}lrrrr@{}}
\caption{\label{tbl-simple}Caption centered above table}\tabularnewline
\toprule()
& mpg & cyl & disp & hp \\
\midrule()
\endfirsthead
\toprule()
& mpg & cyl & disp & hp \\
\midrule()
\endhead
Mazda RX4 & 21.0 & 6 & 160 & 110 \\
Mazda RX4 Wag & 21.0 & 6 & 160 & 110 \\
Datsun 710 & 22.8 & 4 & 108 & 93 \\
Hornet 4 Drive & 21.4 & 6 & 258 & 110 \\
Hornet Sportabout & 18.7 & 8 & 360 & 175 \\
Valiant & 18.1 & 6 & 225 & 105 \\
\bottomrule()
\end{longtable}

>>>>

@@

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, breakable]}{\end{tcolorbox}}\fi

@@

Queen's, simply, produces an immense amount of waste that it is unable
to efficiently manage. The dozens of wards, offices, and kitchens,
serving the hundreds of patients and staff, generates considerable
infectious medical waste, mixed domestic and office waste, and kitchen
waste, which needs to be removed and disposed of daily. Some individual
wards implement waste separation, binning medical wastes separately from
general waste, however separation ends at the point of collection.
Queen's is not served by regular municipal waste collection. What
municipal collection that is done is ad-hoc, sporadic, and based on the
hospital's available financial resources. Rather, most hospital waste
(infectious and non-infectious) is gathered by grounds staff and burnt
at the hospital's incinerator, located at a central point within the
hospital campus\footnote{Sharps are handled and disposed of separately.}
\citep{kalina2020this}. However, the vast majority of the deposited
waste is not incinerated, as a new incinerator provided by the Ministry
of Health in late 2019, is only able to handle a small percentage of the
hospital's waste. Furthermore, the incinerator is frequently inoperable,
under repair, or without power\footnote{There was an older incinerator
  on the grounds which failed in 2017. Between 2017 and 2021, when the
  new incinerator was commissioned, nothing was incinerated at all.}.
Rather, the waste is openly burned, in a constantly smouldering pile to
the side of the incinerator building, sending up the aforementioned
clouds of smoke, which choke the grounds
(Figure~\ref{fig-open-burning}). Innumerable other, smaller, fires,
scattered across the QECH campus (Figure~\ref{fig-map-sensors})
contribute their part, as grounds and maintenance staff habitually burn
leaves and other garden refuse. Furthermore, caregivers\footnote{Patients
  are required to bring a caregiver for in-patient hospitals stays,
  usually a family member, who assist with feeding, bathing, and all
  other non-medical services.} who reside separately on hospital
grounds, cook for themselves throughout the day and night using biomass
(charcoal or wood), and burn their own domestic waste. As a result, air
quality at the hospital is a constant source of discussion, with
patients, staff, and caregivers struggling to cope, when just breathing
is, as the quote used in the title of this article, `unbearable.'

@@

{\centering \includegraphics[width=0.8\textwidth,height=\textheight]{img/open-waste-burning-incinerator-qech.jpg}

@@

\caption{\label{fig-open-burning}Open burning at QECH, with the old
incinerator building in the background (Authors).}

@@

\begin{itemize}
\item
  \textbf{Lions Sight First Eye Hospital}, often shortened to
  \textbf{Lions Sight}, is the largest eye hospital in Malawi and serves
  as the main teaching eye hospital for the Kamuzu University of Health
  Sciences (formerly College of Medicine). It is staffed by 5
  consultants and a team of clinical officers and nurses. It provides a
  mix of public (no cost) and private (at cost) services.
\item
  \textbf{The Blantyre Malaria Project (BMP)}, established by Professors
  Terrie Taylor and Malcolm Molyneux, has carried out clinical research
  and patient care in the area of paediatric malaria, specifically
  cerebral malaria, for more than 30 years\footnote{BMP is credited with
    the development of the Blantyre Coma Score, which is used widely.}.
  Its research infrastructure includes an administrative team, an
  inpatient research ward, an MRI centre, and an outpatient research
  clinic in Ndirande township and in other districts outside of
  Blantyre.
\item
  \textbf{Ward 6B} is a male ward for trauma and orthopaedic patients.
  It was established as part of the original hospital design. It is a
  60-bed ward with a dedicated nursing station and treatment rooms.
\item
  \textbf{The Blantyre Lighthouse Trust Clinic}, also known as
  \textbf{Umodzi Family Centre} or simply, the \textbf{Lighthouse
  Clinic}, is one of four operating across Malawi. The clinics work in
  collaboration with the Ministry of Health (MOH) to provide integrated
  HIV testing, treatment and care for people living with HIV.
\item
  The \textbf{Moyo Nutritional Rehabilitation and Research Unit}, known
  on campus as \textbf{uMoyo}, is a 57-bed nutritional rehabilitation
  unit (NRU) for treating infants and children with severe malnutrition
  and acute illnesses. It is one of 104 operational NRUs in Malawi. It
  also has an outpatient therapeutic feeding program (OTP) for children
  with malnutrition who can be treated outside of the hospital.
\item
  \textbf{Mercy James Institute for Pediatric Surgery and Intensive Care
  (MJC)}, shortened on campus to \textbf{Mercy James}, was opened in
  2017 by the NGO Raising Malawi, which was founded by Madonna. With 3
  operating rooms and 50 beds, it is the first and only first dedicated
  paediatric surgery hospital in Malawi. Prior to its opening, QECH had
  fewer than 10 intensive care beds.
\item
  The \textbf{Administration Building} is the operational hub of the
  campus, containing mostly offices and meeting rooms.
\item
  When a patient arrives at QECH, she or he will usually arrive with a
  guardian: someone to cook for them, buy medicine, do their laundry,
  and help them bathe. The \textbf{Guardian Shelter} is a
  gender-separated concrete floor shelter for sleeping along with a
  cooking pavilion and toilet/shower block are maintained by a the local
  NGO Chira fund. Though simple, the facility is secure and offers one
  of the only free/accessible toilet facilities for visitors on the QECH
  campus.
\end{itemize}

{\centering \includegraphics[width=0.8\textwidth,height=\textheight]{figs/map-sensores-qech-blantyre.png}

\caption{\label{fig-map-sensors}Sensor locations within QECH}

@@

Therefore, for international comparisons and due to the lack of
comprehensive Malawian Standards, we use the WHO recommendations as a
basis of comparison for the measured values
\citep{worldhealthorganization2021who}. The relevant particulate matter
targets are presented in \textbf{?@tbl-who-targets}.

(TODO: REPLACE screenshot)

\begin{table}

\caption{\textbf{?(caption)}}\begin{minipage}[t]{\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics[width=2.04in,height=\textheight]{img/image-replace-table.png}

@@

\end{minipage}%

\end{table}

@@

Due to localised variation (air movement in the immediate area) and the
density of the observations, the plotted 5-minute data obscure
persistent trends. The full set of 5-minute data are plotted and
presented in Appendix A Figure A.1. However, the number of measured
values that exceeded the hazardous limit for both parameters are
summarised in Table~\ref{tbl-peaks}.

\hypertarget{tbl-peaks}{}
\begin{longtable}[]{@{}lrrr@{}}
\caption{\label{tbl-peaks}Peaks for both PM\textsubscript{2.5} and
PM\textsubscript{10} are the number of data points above the WHO interim
target 1 (annual) which is the least stringent; the number of
observations recorded (count) is provided for reference.}\tabularnewline
\toprule()
location & n & pm10 & pm2.5 \\
\midrule()
\endfirsthead
\toprule()
location & n & pm10 & pm2.5 \\
\midrule()
\endhead
Administration & 10900 & 171 & 94 \\
Guardian Shelter & 11032 & 4529 & 5314 \\
Lighthouse Clinic & 11472 & 4365 & 3891 \\
Lions Sight & 11749 & 91 & 14 \\
Malaria & 12031 & 617 & 578 \\
Mercy James & 12193 & 736 & 749 \\
Ward 6B & 11861 & 1113 & 1236 \\
uMoyo & 10637 & 703 & 399 \\
\bottomrule()
\end{longtable}

@@

{\centering \includegraphics{manuscript_files/figure-pdf/fig-24-hour-average-1.pdf}

\caption{\label{fig-24-hour-average}Average 24-hour PM10 and PM2.5 at 8
monitoring stations over 2 months}

@@

Given that the type of fuel and the type of burning (contained vs.~open)
produce very different particulate ``fingerprints'', the ratio of PM10
to PM2.5 values were examined to determine if a clear difference between
locations, and therefore source, could be identified. The results are
presented in Figure~\ref{fig-pm-ratios}.

{\centering \includegraphics{manuscript_files/figure-pdf/fig-pm-ratios-1.pdf}

\caption{\label{fig-pm-ratios}PM10:PM2.5 values for each location. Each
line shows the minimum and maximum ratio for the day based on ratios
calculated hourly. Does not include 14th to 16th October at location
uMoyo due to extreme outliers.}

@@

The relative amount of time exposed to a given category of air quality
is shown in Figure~\ref{fig-percent-exposure}. Each square represents
1\% of the measured time.

{\centering \includegraphics{manuscript_files/figure-pdf/fig-percent-exposure-1.pdf}

\caption{\label{fig-percent-exposure}Percentage of measured values
categorised according to WHO 2021 targets}

@@

\hypertarget{appendix}{%
\section*{Appendix}\label{appendix}}
\addcontentsline{toc}{section}{Appendix}

@@

\hypertarget{appendix-a}{%
\subsection*{Appendix A}\label{appendix-a}}
\addcontentsline{toc}{subsection}{Appendix A}

@@

{\centering \includegraphics{manuscript_files/figure-pdf/fig-5-minute-intervals-1.pdf}

@@

\caption{\label{fig-5-minute-intervals}PM2.5 and PM10 values collected
every 5 minutes over 10 months at 8 locations.}

@@

\hypertarget{appendix-b}{%
\subsection*{Appendix B}\label{appendix-b}}
\addcontentsline{toc}{subsection}{Appendix B}

\hypertarget{hardware-components}{%
\subsubsection*{Hardware Components}\label{hardware-components}}
\addcontentsline{toc}{subsubsection}{Hardware Components}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Raspberry Pi 3 Model B single-board computer technical specifications:
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Broadcom BCM2837 64bit Quad Core Processor powered Single Board
  Computer running at 1.2GHz 1GB RAM
\item
  BCM43438 WiFi on board
\item
  Bluetooth Low Energy (BLE) on board
\item
  40pin extended GPIO
\item
  4 x USB 2 ports 4 pole Stereo output and Composite video port
\item
  Full size HDMI CSI camera port for connecting the Raspberry Pi camera
\item
  DSI display port for connecting the Raspberry Pi touch screen display
\item
  Micro SD port for loading your operating system and storing data
\item
  Upgraded switched Micro USB power source (now supports up to 2.4 Amps)
\item
  Same form factor as the Pi 2 Model B, however the LEDs have changed
  position
\item
  RPI3-MODB-16GB-NOOBS
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Nova PM SDS011 Sensor
\end{enumerate}

\begin{itemize}
\tightlist
\item
  See Data Sheet attachment for technical specifications
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  MCP3008 microchip
\end{enumerate}

\begin{itemize}
\tightlist
\item
  analog-to-digital converter (ADC)
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  Romoss Sense8+ 30000mAh QC Type-C
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Power bank battery
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  Pipe
\end{enumerate}

\begin{itemize}
\tightlist
\item
  clear rubber pipe attainable from any local hardware store
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{5}
\tightlist
\item
  Box
\end{enumerate}

\begin{itemize}
\tightlist
\item
  any box that can fit all the components comfortbaly can be used. The
  box will need to have a whole drilled in it for the pipe.
\end{itemize}

\hypertarget{software-components-and-data-management}{%
\subsubsection*{Software `components' and data
management}\label{software-components-and-data-management}}
\addcontentsline{toc}{subsubsection}{Software `components' and data
management}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The Raspberry Pi operating system runs off of Rasbian software on a
  NOOBS scandisk.
\item
  Air quality monitoring code is written in Python using the
  \href{https://pypi.org/project/python-aqi/}{aqi library} (A library of
  algorithms to convert between AQI value and pollutant concentration).
  The code is stored on the
  \href{https://github.com/opendatadurban/hospital_stations}{Open Data
  Durban GitHub account} and is free for all to access. To be able to
  collect data, the device needs to be connected to a reliable wifi
  network, the SSID and password need to be coded onto the device during
  step 2 in the building method.
\item
  Once the whole device has been put together and placed on site, to
  access that data we use a combination of propgrams:
\end{enumerate}

\begin{itemize}
\tightlist
\item
  \href{https://www.putty.org/}{Putty} - this is an SSH client that we
  use to gain access to the Raspberry Pi from another computer. To be
  able to access the Raspberry Pi in question, the computer in use and
  the air quality monitoring device need to be on the same network for
  the connection to be successful.
\item
  \href{https://winscp.net/eng/download.php}{Winscp} - this is an FTP
  client that we use, in conjunction with Putty, to be able to transfer
  data files from the air quality monitoring device to one's computer.
\item
  \href{https://app.remote.it/}{Remote.it} - this is an application that
  supports remote SSH, so this is used when wanting to access data from
  a device that is not connected to the same network as the computer in
  use. Remote.it is used together with Putty and Winscp to access the
  air quality data remotely.
\end{itemize}

\hypertarget{connectionbuilding-method}{%
\subsubsection*{Connection/building
method}\label{connectionbuilding-method}}
\addcontentsline{toc}{subsubsection}{Connection/building method}

To build the sensor, we followed these steps:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Set up the Raspberry Pi with the Rasbian software using the NOOBS
  scandisk. (insert the scandisk into the Rasberry Pi) A comprehensive
  start up guide can be found here.
\item
  Next we load the code onto the Raspberry Pi. The code can be found on
  the Open Data Durban Hospital Stations Repository Github. To use it
  you can follow the steps in the file called Initiate\_WS.txt. Once all
  the steps have been completed, the Raspberry Pi is now a device that
  can be connected to a particulate matter monitoring sensor.\\
\item
  Connect the hardware components
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Connect the Raspberry Pi to the Nova PM Sensor using the break out
  board that comes with the Sensor.
\item
  Connect the battery to the Raspberry Pi via the micro port
\item
  Attach the rubber pipe to the sensor
\item
  Assemble all components inside the box, with the pipe coming out of
  the drilled hole
\item
  To prevent dirt entering the system, close off all openings between
  the pipe and the box with silicone putty
\item
  Secure box in an elevated position (not too close to the ground) and
  with the pipe facing the direction of the inflow of the air under
  investigation.
\end{itemize}
